\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-05-27 paper/manuscript_jitp_rr.tex
fixed some typos

After preprocessing, our corpus consists of 356,911 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}. The package is hosted on GitHub at ({\em blinded for anonymity}). We have also created an interactive tutorial for texttt{gov2text} hosted on Google Colab \citep{bisong2019google}.

@@

The policy priorities of U.S. mayors are shaped in large part by their partisan affiliations. For example, \citet{einstein2018mayors} finds that Democratic mayors are much more likely than Republicans to support municipal-level redistributive policies, and \citet{einstein2021pictures} finds that Democratic mayors are more likely to support city-level policies aimed at addressing racial inequality. City mayors use government websites to present their policy priorities to the public. Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis. Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with a faith-based initiative to create administrative partnerships with religious organizations. Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}. When Democrat Bart Peterson took office in 2000, the material related to the faith-based initiative was removed from the website.

We illustrate the analysis of municipal website content by studying how differences in website content correlate with the partisanship of the city's mayor. As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance. However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance. These constraints do not apply to website contents. City governments have great discretion in composing their websites, modifying website content is low cost.

@@

We further interpret the STM results using the visualizations we present in Figure \ref{demreptop}. In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. The key implication of our results is that researchers can use the methods we introduce scale up, and lower the cost of, data collection for projects focused on the comparative analysis of website content. Through an application to the analysis of municipal websites in six different state, we find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

>>>>

After preprocessing, our corpus consists of 356,911 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}. The package is hosted on GitHub at ({\em blinded for anonymity}). We have also created an interactive tutorial for \texttt{gov2text} hosted on Google Colab \citep{bisong2019google}.

@@

The policy priorities of U.S. mayors are shaped in large part by their partisan affiliations. For example, \citet{einstein2018mayors} finds that Democratic mayors are much more likely than Republicans to support municipal-level redistributive policies, and \citet{einstein2021pictures} finds that Democratic mayors are more likely to support city-level policies aimed at addressing racial inequality. City mayors use government websites to present their policy priorities to the public. Consider an example; \citet[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis. Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with a faith-based initiative to create administrative partnerships with religious organizations. Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}. When Democrat Bart Peterson took office in 2000, the material related to the faith-based initiative was removed from the website.

We illustrate the analysis of municipal website content by studying how differences in website content correlate with the partisanship of the city's mayor. As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance. However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance. These constraints do not apply to website contents. City governments have great discretion in composing their websites, and modifying website content is low cost.

@@

We further interpret the STM results using the visualizations we present in Figure \ref{fig:demreptop}. In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. The key implication of our results is that researchers can use the methods we introduce to scale up, and lower the cost of, data collection for projects focused on the comparative analysis of website content. Through an application to the analysis of municipal websites in six different states, we find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
